Psychological Needs During Intergroup Contact

### 2021-12-16 Tables/mdlContactGeneral.tex
small tables
Updates from Overleaf
table rotate
line break table fix

\begin{table}
\begin{minipage}[t][\textheight][t]{\textwidth}

@@

@@

$\tau_{11}$ &  &  &  &  &  &  &  &  & 48.94 (PID.OutgroupInteraction)
 7.23 (PID.NonOutgroupInteraction) &  & 40.53 (PID.OutgroupInteraction)
\hspace{1em} 3.43 (PID.NonOutgroupInteraction) & \\
$\rho_{01}$ &  &  &  &  &  &  &  &  & -0.72 (PID.OutgroupInteraction)
 0.12 (PID.NonOutgroupInteraction) &  & -0.70 (PID.OutgroupInteraction)
\hspace{1em}-0.28 (PID.NonOutgroupInteraction) & \\

@@

\end{tabular}

@@

>>>>

\begin{landscape}\begin{table}
\begin{minipage}[t][\textheight][t]{\textwidth}

@@

\resizebox{\linewidth}{!}{

@@

\hspace{1em}$\tau_{11}$ &  &  &  &  &  &  &  &  & 48.94 (PID.OutgroupInteraction)\n 7.23 (PID.NonOutgroupInteraction) &  & 40.53 (PID.OutgroupInteraction)\n 3.43 (PID.NonOutgroupInteraction) & \\
\hspace{1em}$\rho_{01}$ &  &  &  &  &  &  &  &  & -0.72 (PID.OutgroupInteraction)\n 0.12 (PID.NonOutgroupInteraction) &  & -0.70 (PID.OutgroupInteraction)\n-0.28 (PID.NonOutgroupInteraction) & \\

@@

\end{tabular}}

@@

\end{landscape}

### 2021-12-16 Tables/mdlRobustness.tex
small tables
table rotate
line break table fix

$\tau_{11}$ & 0.01 (PID.CoreNeed)
6.05 (PID.OutgroupInteraction) &  & 0.00 (PID.CoreNeed)
46.82 (PID.OutgroupInteraction) &  & 0.01 (PID.CoreNeed)
40.96 (PID.OutgroupInteraction) &  & 0.02 (PID.CoreNeed)
0.20 (PID.Competence)
0.14 (PID.Autonomy)
0.00 (PID.Relatedness) &  & 0.01 (PID.CoreNeed)
0.00 (PID.Competence)
0.00 (PID.Autonomy)
0.00 (PID.Relatedness) &  & 0.05 (PID.CoreNeed)
0.01 (PID.Competence)
0.00 (PID.Autonomy)
\hspace{1em}0.01 (PID.Relatedness) & \\
$\rho_{01}$ & 0.01 (PID.CoreNeed)
-0.27 (PID.OutgroupInteraction) &  & 0.27 (PID.CoreNeed)
-0.68 (PID.OutgroupInteraction) &  & -0.15 (PID.CoreNeed)
-0.68 (PID.OutgroupInteraction) &  & 0.55 (PID.CoreNeed)
-0.15 (PID.Competence)
-0.09 (PID.Autonomy)
 0.56 (PID.Relatedness) &  & -0.16 (PID.CoreNeed)
-0.05 (PID.Competence)
-0.44 (PID.Autonomy)
-0.20 (PID.Relatedness) &  & -0.25 (PID.CoreNeed)
-0.29 (PID.Competence)
-0.23 (PID.Autonomy)
\hspace{1em} 0.02 (PID.Relatedness) & \\
$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & 0.03 (PID.CoreNeed-Autonomy)
-0.93 (PID.Competence-Autonomy)
-0.11 (PID.CoreNeed-Competence)
 0.17 (PID.CoreNeed-Relatedness)
 0.16 (PID.Competence-Relatedness)
-0.10 (PID.Autonomy-Relatedness) &  & 0.60 (PID.CoreNeed-Autonomy)
 0.83 (PID.Competence-Autonomy)
 0.20 (PID.CoreNeed-Competence)
 0.42 (PID.CoreNeed-Relatedness)
-0.79 (PID.Competence-Relatedness)
-0.35 (PID.Autonomy-Relatedness) &  & 0.57 (PID.CoreNeed-Autonomy)
-0.68 (PID.Competence-Autonomy)
 0.09 (PID.CoreNeed-Competence)
-0.27 (PID.CoreNeed-Relatedness)
-0.31 (PID.Competence-Relatedness)
\hspace{1em}-0.08 (PID.Autonomy-Relatedness) & \\

>>>>

\hspace{1em}$\tau_{11}$ & 0.01 (PID.CoreNeed)\n6.05 (PID.OutgroupInteraction) &  & 0.00 (PID.CoreNeed)\n46.82 (PID.OutgroupInteraction) &  & 0.01 (PID.CoreNeed)\n40.96 (PID.OutgroupInteraction) &  & 0.02 (PID.CoreNeed)\n0.20 (PID.Competence)\n0.14 (PID.Autonomy)\n0.00 (PID.Relatedness) &  & 0.01 (PID.CoreNeed)\n0.00 (PID.Competence)\n0.00 (PID.Autonomy)\n0.00 (PID.Relatedness) &  & 0.05 (PID.CoreNeed)\n0.01 (PID.Competence)\n0.00 (PID.Autonomy)\n0.01 (PID.Relatedness) & \\
\hspace{1em}$\rho_{01}$ & 0.01 (PID.CoreNeed)\n-0.27 (PID.OutgroupInteraction) &  & 0.27 (PID.CoreNeed)\n-0.68 (PID.OutgroupInteraction) &  & -0.15 (PID.CoreNeed)\n-0.68 (PID.OutgroupInteraction) &  & 0.55 (PID.CoreNeed)\n-0.15 (PID.Competence)\n-0.09 (PID.Autonomy)\n 0.56 (PID.Relatedness) &  & -0.16 (PID.CoreNeed)\n-0.05 (PID.Competence)\n-0.44 (PID.Autonomy)\n-0.20 (PID.Relatedness) &  & -0.25 (PID.CoreNeed)\n-0.29 (PID.Competence)\n-0.23 (PID.Autonomy)\n 0.02 (PID.Relatedness) & \\
\hspace{1em}$\rho_{00}$ & 0.33 (PID.CoreNeed-OutgroupInteraction) &  & -0.08 (PID.CoreNeed-OutgroupInteraction) &  & 0.01 (PID.CoreNeed-OutgroupInteraction) &  & 0.03 (PID.CoreNeed-Autonomy)\n-0.93 (PID.Competence-Autonomy)\n-0.11 (PID.CoreNeed-Competence)\n 0.17 (PID.CoreNeed-Relatedness)\n 0.16 (PID.Competence-Relatedness)\n-0.10 (PID.Autonomy-Relatedness) &  & 0.60 (PID.CoreNeed-Autonomy)\n 0.83 (PID.Competence-Autonomy)\n 0.20 (PID.CoreNeed-Competence)\n 0.42 (PID.CoreNeed-Relatedness)\n-0.79 (PID.Competence-Relatedness)\n-0.35 (PID.Autonomy-Relatedness) &  & 0.57 (PID.CoreNeed-Autonomy)\n-0.68 (PID.Competence-Autonomy)\n 0.09 (PID.CoreNeed-Competence)\n-0.27 (PID.CoreNeed-Relatedness)\n-0.31 (PID.Competence-Relatedness)\n-0.08 (PID.Autonomy-Relatedness) & \\

### 2021-12-16 Tables/mdlTheory.tex
small tables
table rotate
line break table fix

$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed)
0.04 (PID.Quality) &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & 0.00 (PID.CoreNeed)
0.04 (PID.Quality) &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & 0.03 (PID.CoreNeed)
0.02 (PID.Quality) &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & 0.02 (PID.Allport)
0.02 (PID.Quality) &  & 0.00 (PID.CoreNeed)
\hspace{1em}0.04 (PID.Allport) & \\
$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & 0.37 (PID.CoreNeed)
-0.22 (PID.Quality) &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & -0.18 (PID.CoreNeed)
-0.06 (PID.Quality) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.14 (PID.CoreNeed)
-0.41 (PID.Quality) &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & 0.12 (PID.Allport)
-0.51 (PID.Quality) &  & -1.00 (PID.CoreNeed)
\hspace{1em}-0.07 (PID.Allport) & \\

>>>>

\hspace{1em}$\tau_{11}$ &  &  & 0.05 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed)\n0.04 (PID.Quality) &  & 0.12 (PID.CoreNeed) &  & 0.02 (PID.CoreNeed) &  & 0.00 (PID.CoreNeed)\n0.04 (PID.Quality) &  & 0.09 (PID.CoreNeed) &  & 0.05 (PID.CoreNeed) &  & 0.03 (PID.CoreNeed)\n0.02 (PID.Quality) &  & 0.11 (PID.Allport) &  & 0.05 (PID.Allport) &  & 0.02 (PID.Allport)\n0.02 (PID.Quality) &  & 0.00 (PID.CoreNeed)\n0.04 (PID.Allport) & \\
\hspace{1em}$\rho_{01}$ &  &  & 0.03 (objVar$cor.slope_intercept.) &  & 0.37 (PID.CoreNeed)\n-0.22 (PID.Quality) &  & -0.09 (objVar$cor.slope_intercept.) &  & -0.16 (objVar$cor.slope_intercept.) &  & -0.18 (PID.CoreNeed)\n-0.06 (PID.Quality) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.26 (objVar$cor.slope_intercept.) &  & -0.14 (PID.CoreNeed)\n-0.41 (PID.Quality) &  & -0.07 (objVar$cor.slope_intercept.) &  & -0.19 (objVar$cor.slope_intercept.) &  & 0.12 (PID.Allport)\n-0.51 (PID.Quality) &  & -1.00 (PID.CoreNeed)\n-0.07 (PID.Allport) & \\
